How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-25 tse-paper/content.tex
new study explanation draft

\section{Study Design}

@@

In the following, we present the data set we created for this study,
our study process (presented in \Cref{fig:study}), and the metrics
we measure to answer our research questions.

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of the technique comparison study.}
	\label{fig:study}
\end{figure*}

\subsection{LogChunks}
To conduct the study in this paper, we created the
\emph{LogChunks}  data set~\cite{brandt2020logchunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

\subsection{Study Process}
% FIXME introduce term example
% FIXME mention study figure
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
% motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

\vspace{0.2cm}
\begin{itemize}[leftmargin=0.4cm] \itemsep1em
	\item $|\mbox{True\ Positives}| = \mathit{DesiredLines} \cap
	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
	True positives are lines that appear both in the output of a
	tool as well as what \textit{LogChunks} contains for the
  test example.

@@

% This is a weird position for this paragraph
% TODO What is ``this'' referring to? You just defined a bunch of
%equations.
This concludes one run within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the implemented chunk
retrieval
technique.

\section{Results}
This section first presents the results for each chunk retrieval
technique separately.
Afterwards, we compare the three techniques with each other and to RLR
as a baseline.

>>>>

% TODO -- this is a wrong title -- !!
% TODO find better one
\section{Empirical Comparison Study}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
  % TODO wrong caption!!! find adequate one
	\caption{Design of the technique comparison study.}
	\label{fig:study}
\end{figure*}

% TODO this might need some glue / intro text

\subsection{LogChunks Data Set}
\label{sec:logchunks}
To conduct the study in this paper, we created the
\emph{LogChunks} data set~\cite{brandt2020logchunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, we manually ``labeled
the log part (chunk) describing why the build
failed''.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

This, the build log text, the corresponding chunk,
the search keywords, and the assigned structural categories
make up one \emph{example}.
Examples are the basic units in the training and test sets of our
empirical comparison study.

% TODO: find better title!!!!
\subsection{Study Execution}
\Cref{fig:study} gives an overview over the steps within our empirical
comparison study.
In the following, we each of the steps and the metrics
we measure to answer our research quest

% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...ions.

We apply every one of the four chunk retrieval techniques
% TODO Check abstraction level: leave out acronyms?
(PBE, CTS, KWS, and RLR) on all 80 repositories represented in
\emph{LogChunks} \circlenum{1}.
For each repository, we select training sets of size 1, 2, \dots 5
examples \circlenum{2}.
% For this, we select all examples in \emph{LogChunks}
% (as defined in \Cref{sec:logchunks})
% We begin by selecting all examples
% that correspond to one GitHub repository---and thus the
% same build environment (1).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one?
The test set consists of an example based on the build log produced
chronologically after the build logs in the training set \circlenum{3}.
In this way, we train on examples from past build logs and test on
more recent logs.
% We chose a test set size of 1, as users of the techniques
% should receive reliable results on every build log they analyze.
% M: and why is this important? Doesn't everyone want such stability
%of results?
% C: motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

\vspace{0.2cm}
\begin{itemize}[leftmargin=0.4cm] \itemsep1em
	\item $|\mbox{True\ Positives}| = \mathit{DesiredLines} \cap
	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
	True positives are lines that appear both in the output of a
	technique as well as the chnuk defined in the
  test example.

@@

\section{Results}
% TODO check abstraction level: mention PBE, CTS etc?
This section first presents the results for each chunk retrieval
technique separately.
Afterwards, we compare the three techniques with each other and to a
random baseline.
